Reproducible Research - Assignment 1
========================================================

*Note: I am also using inline code.*

Loading and preprocessing the data
-------------------------------------------------------------------------

```{r LoadAndProcess}
Activity<-read.csv('activity.csv',colClasses = c("integer","Date","integer"))
```


What is mean total number of steps taken per day?
-------------------------------------------------------------------------

I use plyr library.

```{r StepPerDay}
library(plyr)
TotalPerDay<-ddply(Activity,.(date),summarize,sum=sum(steps,na.rm=TRUE))
hist(TotalPerDay$sum,col="blue",xlab="Number of steps per day",main="Frequency of Number of steps per day",breaks=50)
summaryTotal<-summary(TotalPerDay$sum)
```

The mean total per day is **`r summaryTotal["Mean"]`** and the median is **`r summaryTotal["Median"]`**.  

What is the average daily activity pattern?
-------------------------------------------------------------------------

```{r StepDuringDay}
AverageduringDay<-ddply(Activity,.(interval),summarize,Average=mean(steps,na.rm=TRUE))
plot(AverageduringDay$interval,AverageduringDay$Average,type="l",xlab="5 minutes interval",ylab="Average Number of steps",main="Average number of steps during the day")
AverageduringDay[which.max(AverageduringDay$Average),1]
```

The maximum average during the day is during the interval: **`r AverageduringDay[which.max(AverageduringDay$Average),1]`**.



Imputing missing values
-------------------------------------------------------------------------
```{r NANumber}
sum(is.na(Activity$steps))
```

1. There are `r sum(is.na(Activity$steps))` NAs in the dataset.

2. My strategy is to used the mean for that 5-minute interval. To do so I will used the same kind pf dataset as above but expanded for each day/interval.

3. Create the new dataset
```{r FilledNA}
AverageduringDay2<-ddply(Activity,.(interval),summarize,Average=ave(steps,FUN=function(x) mean(x,na.rm=TRUE)))
ActivityFilled<-data.frame(steps=ifelse(is.na(Activity$steps),AverageduringDay2$Average,Activity$steps),date=Activity$date,interval=Activity$interval)
TotalPerDayFilled<-ddply(ActivityFilled,.(date),summarize,sum=sum(steps,na.rm=TRUE))
hist(TotalPerDayFilled$sum,col="blue",xlab="Number of steps per day",main="Frequency of Number of steps per day",breaks=50)
summaryTotalFilled<-summary(TotalPerDayFilled$sum)
```

The mean total per day is **`r summaryTotalFilled["Mean"]`** and the median is **`r summaryTotalFilled["Median"]`**, both are HIGHER than the values for the NAs-included dataset.


Are there differences in activity patterns between weekdays and weekends?
-------------------------------------------------------------------------

1 For splitting between Weekday and weekend, I will do a first factorization with the weekday function then a second factorization on the latter level.

```{r DayFactor}
factor1<-factor(weekdays(Activity$date),levels=c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))
factor2<-factor(ifelse(unclass(factor1)<6,"Weekday","Weekend"))
ActivityPerDayType<-data.frame(steps=Activity$steps,date=Activity$date,interval=Activity$interval,DayLevel=factor2)
```

2 Plotting
```{r plotting}
library(lattice)
AverageduringDayType<-ddply(ActivityPerDayType,.(DayLevel,interval),summarize,Average=mean(steps,na.rm=TRUE))
xyplot(AverageduringDayType$Average~AverageduringDayType$interval|AverageduringDayType$DayLevel,layout=c(1,2),type="l",ylab="Average number of steps per day",xlab="5 minutes interval")
```